---
title: "Developing Data Products Week4 Project"
author: "SiranC"
output: 
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: default
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Instructions

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

Your Shiny Application

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

The application must include the following:

1. Some form of input (widget: textbox, radio button, checkbox, ...)
2. Some operation on the ui input in sever.R
3. Some reactive output displayed as a result of server calculations
4. You must also include enough documentation so that a novice user could use your application.
5. The documentation should be at the Shiny website itself. Do not post to an external link.

## Project Review

In this project, the Canada COVID-19 cases data from [Government of Canada]( https://health-infobase.canada.ca/covid-19/) was used to create a Shiny application showing the case number of COVID-19 cross the country by 09/20/2020.

## Data Process

```{r, echo=TRUE, message=FALSE}
library(dplyr)
library(lubridate)

covid <- read.csv('covid19.csv', stringsAsFactors= FALSE, header = TRUE)
covid <- covid %>%
    select(pruid, prname,date,numconf,numdeaths,numtotal,numtested,numrecover)
covid$date <- parse_date_time(covid$date, orders = c("ymd", "dmy", "mdy"))

head(covid)
```

## Shiny Application

```{r, echo = FALSE, fig.fullwidth=TRUE}
library(shiny)
library(dplyr)
library(lubridate)

#Data loading
covid <- read.csv('covid19.csv', stringsAsFactors= FALSE, header = TRUE)
covid <- covid %>%
    select(pruid, prname,date,numconf,numdeaths,numtotal,numtested,numrecover)
covid$date <- parse_date_time(covid$date, orders = c("ymd", "dmy", "mdy"))

# Define UI for application
ui <- fluidPage(
        #Application Title
        titlePanel("COVID-19 Cases in Canada"),
        
        #Sidebar with multiple slider input
        sidebarLayout(
            sidebarPanel(
                dateRangeInput('date',strong('Select a Period:'),
                               start = '2020-01-31', end = '2020-09-20',
                               min = '2020-01-31', max = '2020-09-20'
                ),
                
                selectInput('region',strong('Select a Region'),
                            c('Canada','British Columbia','Manitoba','New Brunswick',
                              'Newfoundland and Labrador','Northwest Territories',
                              'Nova Scotia', 'Nunavut','Ontario','Prince Edward Island',
                              'Quebec','Repatriated travellers','Saskatchewan','Yukon')
                ),
                
                radioButtons('data_type','Select a data type',
                             c('numconf','numdeaths','numtotal','numtested',
                               'numrecover')
                )
            ),
            
            mainPanel(
                h3("The Progression of COVID-19 Cases in Canda"),
                plotOutput("distPlot"),
                h3('Data Summary'),
                verbatimTextOutput('view'),
                tags$a(href = "https://health-infobase.canada.ca/covid-19/", 
                       "Source: Government of Canada", target = "_blank")
            )
        )
    )

# Define server logic required to plot the data
server <- function(input, output) {

    # subset data
    selected_data <- reactive({
        covid %>%
            select(prname,date,input$data_type)%>%
            filter(prname == input$region,
                   date >= as.POSIXct(input$date[1]) & date <= as.POSIXct(input$date[2]))
    })
    
    output$distPlot <- renderPlot({
        plot(x =  selected_data()$date, y = selected_data()[,3],
             type = 'l', lwd = 2, xlab = 'Date', 
             ylab = paste('Number of Cases in',input$region),
             col = 'purple')
    })
    
    output$view <- renderPrint({
        summary(selected_data())
    })
}

# Run the application 
shinyApp(ui = ui, server = server)
```

